Figures

### 2019-05-13 figures/06_lulc_buffer_demo.Rmd
recolor cdl figs

```{r cdl_viewport, fig.height=5}
library(raster)
library(dplyr)
library(stars)

@@

g_bar <- ggplot() + 
  geom_col(data = test2, aes(x = category, 
                             y = percent, 
                             fill = category)) +
  theme(legend.direction = "horizontal", 
        legend.position = 0,
        axis.text.x = element_text(angle = 90)) +
  guides(fill = guide_legend(ncol = 2)) +
  ggtitle("CDL llid = 2745")

@@

cdl_df <- as.data.frame(r, xy = TRUE) %>%
  dplyr::select(x, y, contains("2745"))
names(cdl_df)[3] <- "value"
cdl_df <- left_join(cdl_df, cdl_key, by = c("value" = "code")) 
cdl_df <- dplyr::filter(cdl_df, !is.na(category), 
                        category %in% test2$category)

g_raster <- ggplot() + 
  geom_raster(data = cdl_df, aes(x = x, y = y, fill = category)) +
  theme_void()

>>>>

```{r cdl_viewport, fig.height=5}
library(raster)
library(dplyr)

@@

color_key <- data.frame(category = test2$category, 
                         color_cat = c("ag", "ag", "ag", "ag", "ag", "ag", 
                                       "water", "dev", "forest"),
                         color = c(
                           RColorBrewer::brewer.pal(6, "YlOrBr"), 
                           "#9ecae1", "#000000", "#2ca25f"),
                        stringsAsFactors = FALSE)
color_key <- arrange(color_key, color_cat)

test2 <- left_join(test2, color_key)
test2$category <- factor(test2$category, levels = color_key$category)

g_bar <- 
    ggplot() + 
  geom_col(data = test2, aes(x = category, 
                             y = percent, fill = category)) +
    scale_fill_manual(values = setNames(color_key$color, color_key$category)) +
  theme(legend.direction = "horizontal", 
        legend.position = 0,
        axis.text.x = element_text(angle = 90)) +
  guides(fill = guide_legend(ncol = 2)) +
  ggtitle("CDL llid = 2745")

@@

cdl_df <- as.data.frame(r, xy = TRUE) %>%
  dplyr::select(x, y, contains("2745"))
names(cdl_df)[3] <- "value"
cdl_df <- left_join(cdl_df, cdl_key, by = c("value" = "code")) 
cdl_df <- dplyr::filter(cdl_df, !is.na(category), 
                        category %in% test2$category)
cdl_df$category <- factor(cdl_df$category, levels = color_key$category)

g_raster <- ggplot() + 
  geom_raster(data = cdl_df, aes(x = x, y = y, fill = category)) +
  scale_fill_manual(values = setNames(color_key$color, 
                                      color_key$category)) +
  theme_void()
